---
title: "assignment-b4"
output: html_document
date: "2024-12-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(purrr)
library(janeaustenr)
library(tidytext)
library(tidyverse)
```

## Exercise 1

### Task: Develop a plot of the most commonly used words in the Jane Austen novel "Pride and Prejudice"

Step 1: Tidying Character Data

```{r}
words <- prideprejudice %>% 
  paste(collapse = " ") %>% 
  str_remove_all("\\d") %>% 
  str_remove_all("[[:punct:]]") %>% 
  str_squish() %>% 
  str_split("\\s+") %>%
  unlist() %>% 
  tolower() %>% 
  .[!. %in% stop_words$word] 
```

Step 2: Plotting the Most Common Words

```{r}
word_freq <- table(words)
top10 <- sort(word_freq, decreasing = TRUE)[1:50]
wordcloud(names(top10), freq = top10, min.freq = 1, 
          scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"))
```


## Exercise 2

### Task: Make a function that converts words into your own version of pig latin

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
